---
title: "Download_Data"
author: "Alan Jackson"
date: "2022-11-11"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(GeocodeHou)
library(postmastr)

google_crs <- "EPSG:4326" # lat long
CoH_crs <- "EPSG:2278" # X-Y

bbox <- osmdata::getbb(place_name = "Houston")

# leaflet::leaflet() %>% 
#   leaflet::addTiles() %>% # OpenStreetMap by default
#   leaflet::addCircleMarkers(data=a, 
#                    radius=2, 
#                    color="black",
#                    opacity=1,
#                    fillOpacity = 1)

knitr::opts_chunk$set(echo = TRUE)
```

##        Get census tracts

```{r tracts}

path <- "/home/ajackson/Dropbox/Rprojects/Curated_Data_Files/Census_data/"

Pop <- readRDS(paste0(path, "Pop_data_by_block_2020.rds"))
ACS <- readRDS(paste0(path, "Income_and_Age_by_BlkGrp_2015_2020.rds"))

Pop <- 
  Pop %>%
  mutate(area=sf::st_area(geometry)) %>% 
  mutate(area=units::drop_units(area)) %>% 
  mutate(Pop_density=(Pop/area)*2.59e+6) %>% 
  mutate(Pop_density=ifelse(Pop<10, NA, Pop_density))

Pop %>% 
  ggplot(aes(x=area, y=Pop)) +
  geom_point()

#   Let's look at income to decide where to sample

ACS %>% 
  ggplot(aes(x=Per_cap_incE))+
  geom_histogram()

bins <- c(0, 20000, 40000, 60000, 80000, 100000, Inf)
pal <- leaflet::colorBin("YlOrRd", domain = ACS$Per_cap_incE, bins = bins)

leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=sf::st_transform(ACS,crs=google_crs),
                       opacity=5,
                       fillOpacity=0.4,
                       color="red",
                       fillColor = ~pal(Per_cap_incE),
                       popup = ~as.character(Per_cap_incE),
                       weight=1,
                      #  label = ~as.character(Med_incE),
                      # labelOptions = leaflet::labelOptions(
                      #   style = list("font-weight" = "normal", padding = "3px 8px"),
                      #   textsize = "15px",
                      #   direction = "auto")
                      ) %>% 
  leaflet::addLegend(data=sf::st_transform(ACS,crs=google_crs),
                     pal = pal, values = ~Per_cap_incE, opacity = 0.7, 
                     title = "Avg Income", position = "bottomright")



#   Let's look at density to decide where to sample

Pop %>% 
  ggplot(aes(x=Pop_density))+
  geom_histogram()

bins <- c(0, 2000, 5000, 10000, 20000, 50000, Inf)
pal <- leaflet::colorBin("YlOrRd", domain = Pop$Pop_density, bins = bins)

leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=sf::st_transform(Pop,crs=google_crs),
                       opacity=0,
                       fillOpacity=0.4,
                       color="red",
                       fillColor = ~pal(Pop_density),
                       popup = ~paste("Den=",
                                     as.character(round(Pop_density)),
                                     "\nPop=",
                                     as.character(Pop)),
                       weight=1,
                      #  label = ~as.character(Med_incE),
                      # labelOptions = leaflet::labelOptions(
                      #   style = list("font-weight" = "normal", padding = "3px 8px"),
                      #   textsize = "15px",
                      #   direction = "auto")
                      ) %>% 
  leaflet::addLegend(data=sf::st_transform(Pop,crs=google_crs),
                     pal = pal, values = ~Pop_density, opacity = 0.7, 
                     title = "People per sq mi", position = "bottomright")



```


```{r}

#   What features are available?
osmdata::available_features()
#   What tags are available?
osmdata::available_tags("amenity") 

# big_streets <- 
#   osmdata::getbb(place_name = "Houston") %>% 
#   osmdata::opq()%>% # Build query
#   osmdata::add_osm_feature(key = "highway", 
#                   value = c("motorway", 
#                             "motorway_link" 
#                             )) %>% # select the big roads
#   osmdata::osmdata_sf(quiet=FALSE) 

parking <- 
  osmdata::getbb(place_name = "Houston") %>% 
  #tmaptools::bb(Small_bbox, output="matrix") %>% # turn bounding box into matrix
  osmdata::opq(timeout = 50) %>% # Build query
  osmdata::add_osm_feature(key = "amenity", 
                           value = "parking" 
                            ) %>% 
  osmdata::osmdata_sf(quiet=FALSE) # turn into an sf file
  
ggplot() +
  geom_sf(data = parking$osm_polygons,
          inherit.aes = FALSE,
          fill="steelblue",
          color = "steelblue") +
  #   coord_sf needs to follow all the geom_sf statements
  coord_sf(xlim = c(bbox[1,1], bbox[1,2]),
           ylim = c(bbox[2,1], bbox[2,2]),
           expand = FALSE,
           default_crs=google_crs)  

leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=parking$osm_polygons,
                   opacity=0,
                   fillOpacity = 1) %>% 
  leaflet::addPolygons(data=sf::st_transform(ACS,crs=google_crs),
                       opacity=5,
                       fillOpacity=0,
                       color="red",
                       weight=1)



```

##  Make buffers

```{r buffers}

#   Start at 19th and Shepherd, east to Yale, south to 11th, west to Shepherd

Buffer_coord <- as_tibble(rbind(c(29.802783, -95.410146),
                      c(29.802935, -95.399204),
                      c(29.790674, -95.398971),
                      c(29.790514, -95.409865),
                      c(29.802783, -95.410146)))
lines <- Buffer_coord %>%
  sf::st_as_sf(coords = c("V2", "V1"), crs = google_crs) %>%
  summarise(geometry = sf::st_combine(geometry)) %>%
  sf::st_cast("LINESTRING")

Buffer300 <- lines %>% #  5 minute walk
  sf::st_transform(crs=CoH_crs) %>% 
  sf::st_line_sample(n=250) %>% 
  sf::st_buffer(dist=1000)

Buffer1000 <- lines %>% 
  sf::st_transform(crs=CoH_crs) %>% 
  sf::st_line_sample(n=250) %>% 
  sf::st_buffer(dist=3000)

Buffer2000 <- lines %>% 
  sf::st_transform(crs=CoH_crs) %>% 
  sf::st_line_sample(n=250) %>% 
  sf::st_buffer(dist=6000)



leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=sf::st_transform(Buffer300, crs=google_crs),
                   opacity=0.5,
                   fillOpacity = 0.3) %>% 
  leaflet::addPolygons(data=sf::st_transform(Buffer1000, crs=google_crs),
                       color="red",
                   opacity=0.5,
                   fillOpacity = 0.3) %>%  
  leaflet::addPolygons(data=sf::st_transform(Buffer2000, crs=google_crs),
                       color="green",
                   opacity=0.5,
                   fillOpacity = 0.3) 

```

##  People close to parking lots

- Extract the parking lots in the Heights
- Look at the area distribution and the aspect ratio
- Select out the larger, rounder lots
- Create centroids
- Calculate buffers for each lot at 1000, 2000, and 4000 feet
- Intersect with census blocks and calc population in each buffer


```{r parking vs pop}

#  Create AOI box

bbox <- basemapR::expand_bbox(sf::st_bbox(sf::st_transform(lines, crs=CoH_crs)),
                              X=150, Y=300, crs_out=google_crs)

#   Extract parking lots in the box

Parking_TF <- sf::st_contains( sf::st_transform(
                                    sf::st_as_sfc(bbox, crs=google_crs),
                                    crs=CoH_crs),
                               sf::st_transform(
                                    sf::st_as_sfc(parking$osm_polygons,
                                              crs=google_crs),
                                    crs=CoH_crs))

Parking_bb <- parking$osm_polygons[unlist(Parking_TF),]

Parking_bb %>% 
leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons( 
    weight=1,
    opacity=0.5, fillOpacity = 0.5) %>% 
  leaflet::addPolygons(data=sf::st_as_sfc(bbox, crs=google_crs), 
    weight=3,
    color="red",
    opacity=0.5, fillOpacity = 0.0) %>% 
  leaflet::addPolygons(data=sf::st_as_sfc(lines, crs=google_crs), 
    weight=3,
    color="green",
    opacity=0.5, fillOpacity = 0.0)  

```

##        Area distribution

Note there are 325 sq ft per parking space.

```{r areas}

Parking_bb <- Parking_bb %>%
  mutate(P_area=units::drop_units(sf::st_area(.))*10.764) %>% 
  select(osm_id, P_area)

# Areas <- sf::st_area(Parking_bb) %>% units::drop_units() %>% 
#   enframe() %>% mutate(value=value*10.764)

Parking_bb %>% 
  filter(P_area<20000) %>% 
  ggplot(aes(x=P_area)) + 
  geom_histogram()

#   Approximate number of parking spaces
sum(Parking_bb$P_area)/325

# Poly_len <- function(poly){
#   
# }
# 
# Aspect <- function(polys){
#   Max_len <- polys %>%
#     group_by(osm_id) %>% 
#       sf::st_cast('MULTIPOINT') %>% 
#       sf::st_cast('POINT') %>% 
#       summarize(dist=max(sf::st_distance(.))) #%>% 
#     units::drop_units() %>% 
#       enframe() %>% 
#     mutate(value=max(value)) %>% 
#       #mutate(value=max(value)) %>% 
#     mutate(value=value*3.28084)  
#     
#   Areas <- polys %>% 
#     sf::st_area() %>% 
#     units::drop_units() %>% 
#     enframe() %>% 
#     mutate(value=value*10.764)
#   
#   cbind(Areas, Max_len)
# }

# Aspect(Parking_bb)

```
##   Create centroids and buffers


```{r centroids}

Centroids <- sf::st_centroid(Parking_bb)

Lot_buffer_1000 <-  Centroids %>% #  5 minute walk
  sf::st_transform(crs=CoH_crs) %>% 
  sf::st_buffer(dist=1000) %>% 
  sf::st_transform(crs=google_crs) 

Parking_bb %>% 
leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons( 
    weight=1,
    opacity=0.5, fillOpacity = 0.5) %>% 
  leaflet::addPolygons(data=sf::st_as_sfc(Lot_buffer_1000, crs=google_crs), 
    weight=3,
    color="red",
    opacity=0.5, fillOpacity = 0.0)

```

##    Intersect buffers with census data

```{r census}

#   Calculate %area of each block in buffer

Test_Pop <- Pop %>%  # Clean up file and transform to XY
  select(GEOID, Households, Households_occ, starts_with("Pop")) %>% 
  sf::st_transform(crs=CoH_crs) %>% 
  mutate(area=units::drop_units(sf::st_area(.))) # note area is sq ft

#   Trim census file to AOI
Contains <-   sf::st_contains(Buffer2000, Test_Pop)
Test_Pop <- Test_Pop[unlist(Contains),]

Test_buff <- Lot_buffer_1000 %>% # Clean up file and transform to XY
  select(osm_id) %>% 
  sf::st_transform(crs=CoH_crs)

Test_out <- sf::st_intersection(Test_Pop, Test_buff) %>% 
  mutate(Overlap_area = units::drop_units(sf::st_area(geometry))) %>%  # units of ft^2
  filter(Overlap_area>10) %>% # remove boundary issues
  mutate(HH_frac=Households*Overlap_area/area,
         Pop_frac=Pop*Overlap_area/area)

Test_out %>% group_by(GEOID) %>% filter(n()>1)

Diffs <- Test_Pop[!(Test_Pop$GEOID %in% Test_out$GEOID),]

leaflet::leaflet() %>% 
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=sf::st_transform(Test_buff,crs=google_crs),
                   color="red",
                   opacity=1,
                   weight=2.5,
                   popup = ~osm_id,
                   fillOpacity = 0.01) %>% 
  leaflet::addPolygons(data=sf::st_transform(Test_Pop,crs=google_crs), 
                   color="black",
                   opacity=1,
                   weight=0.5,
                   popup = ~GEOID,
                   fillOpacity = 0.01)

```
##   Calc in each buffer

Largest parking lots have the smallest draw on local population
(Who wants to live next to a huge parking lot?)

There are plenty of people within a 5 minute walk. Why aren't they supported?

Need:

- restrooms
- sidewalks
- shade
- slower traffic
- more stop signs and stoplights
- bike racks or cages
- bike lanes
- frequent and reliable transit


```{r calc pop in buffer}

#   Collapse Test_out by parking lot id

Buffer_pop <- Test_out %>%
  sf::st_drop_geometry() %>% # not needed and this speeds things a lot
  group_by(osm_id) %>% 
    summarize(Pop=sum(Pop_frac, na.rm=TRUE),
              HH =sum(HH_frac,  na.rm=TRUE))

Final_buff1000 <- left_join(Buffer_pop,
                            sf::st_drop_geometry(Parking_bb),
                            by="osm_id") %>% 
  mutate(Parking_space=P_area/325)

Final_buff1000 %>% 
  ggplot(aes(x=Parking_space, y=Pop)) + 
  geom_point() +
  labs(title="Population Within a 5 Minute Walk vs. Number of Spaces",
       x="Number of Parking Spaces (using 325 sq-ft per space)",
       y="Population from 2020 Census within 1000 Feet")

Final_buff1000 %>% 
  ggplot(aes(x=Parking_space, y=HH)) + 
  geom_point() +
  labs(title="Households Within a 5 Minute Walk vs. Number of Spaces",
       x="Number of Parking Spaces (using 325 sq-ft per space)",
       y="Households from 2020 Census within 1000 Feet")



```

##    Find parking near the most people, and how many people close to largest lot.

The parking near the most people has a high-rise low income retirement home and
an apartment complex within 1000 feet. There are about 800 people who live an
easy walk from that spot, in the NW corner of the study area.

Diagonally opposite are the largest parking lots. One of the largest, next to a
shopping center, has only 450 people within an easy walk, and has about 300
parking spaces - which are never full. A big issue is that the entire area
between Shepherd and Durham is basically a wasteland of parking lots, large
stores, and car dealerships. Little housing, though up by 20th street that is
changing with newly constructed apartment complexes.

```{r biggest and most}

osm_max <- "1112562906"
osm_max2 <- "1112417014"
osm_lot <- "1113421679"

Two_buffer_1000 <-  Centroids %>%
  filter(osm_id %in% c(osm_max, osm_max2, osm_lot)) %>% 
  sf::st_transform(crs=CoH_crs) %>% 
  sf::st_buffer(dist=1000) %>% 
  sf::st_transform(crs=google_crs) 

Two_lots <- Parking_bb %>% 
  filter(osm_id %in% c(osm_max, osm_max2,  osm_lot))  

Two_lots %>% 
leaflet::leaflet() %>%
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons( 
    weight=1,
    opacity=0.5, fillOpacity = 0.5) %>% 
  leaflet::addPolygons(data=sf::st_as_sfc(Two_buffer_1000, crs=google_crs), 
    weight=3,
    color="red",
    opacity=0.5, fillOpacity = 0.0)
```





##   Taxes lost due to parking lots

```{r lost taxes}

Hcad_path <- "/home/ajackson/Dropbox/Rprojects/Curated_Data_Files/"
df <- readRDS(paste0(Hcad_path, "HCAD/Values_2022.rds"))

#   First pare down file by zipcode

df <- df %>% 
  filter(site_addr_3=="77008")

#   Pull out just the commercial properties

df <- df %>% 
  filter(state_class=="F1")

#   Calculate some stuff

df <- df %>% 
  mutate(bld_ar=as.numeric(bld_ar)) %>% 
  mutate(land_ar=as.numeric(land_ar)) %>% 
  mutate(bld_val=as.numeric(bld_val)) %>% 
  mutate(land_val=as.numeric(land_val)) %>% 
  mutate(ratio_area=bld_val/land_val) %>% 
  mutate(ratio_value=bld_val/land_val) %>% 
  mutate(bld_persqft=bld_val/bld_ar) %>% 
  mutate(land_persqft=land_val/land_ar) %>% 
  filter(bld_ar>500) %>% 
  filter(land_ar>1000) %>% 
  filter(land_val>0)
  

#   How big are the commercial buildings?

df %>% 
  ggplot(aes(x=bld_ar)) +
  geom_histogram() +
  labs(title="Building Areas in Zip 77008",
       x="Area (sq ft)")

#   Value per sq foor for buildings

df %>% 
  ggplot(aes(x=bld_persqft)) +
  geom_histogram() +
  labs(title="Building Value per Square Foot in Zip 77008",
       x="Dollars per sq-ft")

#   Value per sq foor for land

df %>% 
  ggplot(aes(x=land_persqft)) +
  geom_histogram(bins=20) +
  labs(title="Land Value per Square Foot in Zip 77008",
       x="Dollars per sq-ft")

```

##   attach lat longs to tax data

```{r geocode}

#   Break out address components

foo <- df %>% mutate(site_addr_1=stringr::str_remove(site_addr_1, " \\d+$")) 
foo <- pm_identify(foo, var="site_addr_1") # add ID fields
foo2 <- pm_prep(foo, var="site_addr_1", type="street") # Prep data
foo2 <- pm_houseFrac_parse(foo2)
foo2 <- pm_house_parse(foo2)
foo2 <- pm_streetDir_parse(foo2)
foo2 <- pm_streetSuf_parse(foo2)
foo2 <- pm_street_parse(foo2)
foo2 <- foo2 %>% 
  mutate(pm.street=str_to_upper(pm.street)) %>% 
  mutate(pm.street=str_replace(pm.street, " AT ", "/")) %>% 
  mutate(pm.streetSuf=str_to_upper(pm.streetSuf)) %>% 
  mutate(pm.preDir=replace_na(pm.preDir, "")) %>% 
  mutate(pm.sufDir=replace_na(pm.sufDir, "")) %>% 
  mutate(pm.streetSuf=replace_na(pm.streetSuf, ""))
foo <- pm_replace(foo2, source=foo)

#   Geocode

match <- NULL
unmatch <- NULL
for (i in 1:nrow(foo)){ # exact match
  if (is.na(foo[i,]$pm.street)) {next}
  print(paste("i=",i))
  tmp <- GeocodeHou::match_exactly(foo[i,]$pm.house, 
                        foo[i,]$pm.preDir,
                        foo[i,]$pm.street,
                        foo[i,]$pm.streetSuf, 
                        foo[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match <- cbind(foo[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch <- cbind(foo[i,], Fail=tmp$Fail) %>% 
      rbind(., unmatch)
  }
}

#   Bad street type

match_type <- NULL
unmatch_type <- NULL
foo2 <- unmatch %>% filter(Fail=="Street_type")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_type(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_type <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_type)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_type <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_type)
  }
}

#   Bad street number

match_numb <- NULL
unmatch_numb <- NULL
foo2 <- unmatch %>% filter(Fail=="Street_num")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_number(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_numb <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_numb)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_numb <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_numb)
  }
}


#   Bad street prefix

match_pre <- NULL
unmatch_pre <- NULL
foo2 <- unmatch %>% filter(Fail=="Prefix")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_prefix(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_pre <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_pre)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_pre <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_pre)
  }
}

#     Combine all for final set

foo2 <- rbind(match_numb, match_pre, match_type) %>% 
  select(-starts_with("pm"), -Fail)

df2 <- match %>% 
  select(-starts_with("pm")) %>% 
  rbind(., foo2)
  

```

##        Pull out only the tax data near my square

```{r limit to streets}

#   Extract tax data in the box

Tax_data <- sf::st_transform(
                sf::st_as_sf(df2, coords = c("Lon", "Lat"), crs = google_crs),
                  crs=CoH_crs)

tmp <- sf::st_contains( Buffer300, Tax_data)

Tax_data <- Tax_data[unlist(tmp),]

leaflet::leaflet() %>% 
  leaflet::addTiles() %>% # OpenStreetMap by default
  leaflet::addPolygons(data=sf::st_transform(Parking_bb, crs=google_crs),
                   color="blue",
                   opacity=1,
                   weight=.5,
                   popup = ~osm_id,
                   fillOpacity = 0.5) %>% 
  leaflet::addCircleMarkers(data=sf::st_transform(Tax_data,crs=google_crs), 
                   popup = ~as.character(bld_ar),
                   radius=2, 
                   color="black",
                   opacity=1,
                   fillOpacity = 1)
```

##        Distribution of $ per sq foot for commercial property

The distribution of value per square foot is quite wide, but there is a distinct
clustering by age - not surprisingly newer building are generally more valuable
than older buildings.

For buildings built before 2000, the mean value is $50 per sq-ft, and the median
value is $38 per sq-ft. For newer buildings, 2000 and more recent, the same 
values are $115 and $120 respectively. For land value the distribution is very
tight, and the value is $68 per sq-ft.

```{r dollars per sqft}

Tax_data %>% 
  ggplot(aes(x=bld_persqft)) +
  geom_histogram()

#   bld_ar is floor space

Tax_data %>% 
  ggplot(aes(x=bld_ar)) +
  geom_histogram()

Tax_data %>% 
  ggplot(aes(x=land_persqft)) +
  geom_histogram()

Tax_data %>% 
  mutate(yr_impr=as.numeric(yr_impr)) %>% 
  ggplot(aes(x=bld_persqft, y=yr_impr)) + 
  geom_point() +
  geom_smooth(method="lm")

Tax_data %>% 
  filter(yr_impr>=2000) %>% 
  summary()

Tax_data %>% 
  filter(yr_impr<2000) %>% 
  summary()

Tax_data %>% 
  mutate(tranche=if_else(yr_impr<2000,"Before 2000", "After 2000")) %>% 
  sf::st_drop_geometry() %>% 
  group_by(tranche) %>% 
    summarize(Mean_val=round(mean(bld_persqft)),
              Med_val =round(median(bld_persqft)),
              StdDev  =round(sd(bld_persqft)),
              NumVal  =n()) %>% 
  arrange(desc(tranche)) %>% 
  gt::gt() %>% 
  gt::tab_header(
    title="Values per Square Foot",
    subtitle="Commercial Buildings in the Heights"
  ) %>% 
  gt::fmt_currency(
    columns=c(Mean_val,	Med_val,	StdDev)
  ) %>% 
  gt::cols_label(
    tranche="Year Range",
    Mean_val="Mean",
    Med_val="Median",
    StdDev="Std Dev",
    NumVal="Samples"
  )

```

##    Lost taxes

```{r lost revenue}

Building_value <- 115 # dollars per sq foot

Tax_rate <- sum(1.037200, 0.343730, 0.030550, 0.007990, 0.148310, 0.004900,
                0.095569, 0.533640)/100

Taxes <- Parking_bb %>% 
  sf::st_drop_geometry() %>% 
  mutate(Value=P_area*Building_value) %>% 
  mutate(Taxes=Value*Tax_rate)

Taxes %>% ggplot(aes(x=Value))+
  geom_histogram()

Taxes %>% ggplot(aes(x=Taxes))+
  geom_histogram()

sum(Taxes$Taxes)

```


##    interlude for old buildings


```{r old buildings}

Old <- readRDS(paste0(Hcad_path, "HCAD/Values_2022.rds")) %>% 
  mutate(yr_impr=as.numeric(yr_impr)) 

Old <- Old %>% 
  filter(yr_impr>1860 & yr_impr<1910)

#   Break out address components

foo <- Old %>% mutate(site_addr_1=stringr::str_remove(site_addr_1, " \\d+$")) 
foo <- pm_identify(foo, var="site_addr_1") # add ID fields
foo2 <- pm_prep(foo, var="site_addr_1", type="street") # Prep data
foo2 <- pm_houseFrac_parse(foo2)
foo2 <- pm_house_parse(foo2)
foo2 <- pm_streetDir_parse(foo2)
foo2 <- pm_streetSuf_parse(foo2)
foo2 <- pm_street_parse(foo2)
foo2 <- foo2 %>% 
  mutate(pm.street=str_to_upper(pm.street)) %>% 
  mutate(pm.street=str_replace(pm.street, " AT ", "/")) %>% 
  mutate(pm.streetSuf=str_to_upper(pm.streetSuf)) %>% 
  mutate(pm.preDir=replace_na(pm.preDir, "")) %>% 
  mutate(pm.sufDir=replace_na(pm.sufDir, "")) %>% 
  mutate(pm.streetSuf=replace_na(pm.streetSuf, ""))
foo <- pm_replace(foo2, source=foo)

#   Geocode

match <- NULL
unmatch <- NULL
for (i in 1:nrow(foo)){ # exact match
  if (is.na(foo[i,]$pm.street)) {next}
  print(paste("i=",i))
  tmp <- GeocodeHou::match_exactly(foo[i,]$pm.house, 
                        foo[i,]$pm.preDir,
                        foo[i,]$pm.street,
                        foo[i,]$pm.streetSuf, 
                        foo[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match <- cbind(foo[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch <- cbind(foo[i,], Fail=tmp$Fail) %>% 
      rbind(., unmatch)
  }
}
#   Bad street type

match_type <- NULL
unmatch_type <- NULL
foo2 <- unmatch %>% filter(Fail=="Street_type")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_type(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_type <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_type)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_type <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_type)
  }
}

#   Bad street number

match_numb <- NULL
unmatch_numb <- NULL
foo2 <- unmatch %>% filter(Fail=="Street_num")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_number(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_numb <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_numb)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_numb <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_numb)
  }
}


#   Bad street prefix

match_pre <- NULL
unmatch_pre <- NULL
foo2 <- unmatch %>% filter(Fail=="Prefix")
for (i in 1:nrow(foo2)){ # name repair
  print(paste("i=",i))
  tmp <- GeocodeHou::repair_prefix(foo2[i,]$pm.house, 
                        foo2[i,]$pm.preDir,
                        foo2[i,]$pm.street,
                        foo2[i,]$pm.streetSuf, 
                        foo2[i,]$site_addr_3)
  if (tmp$Success){ #   success
    print(paste("Success", tmp$Lat, tmp$Lon))
    match_pre <- cbind(foo2[i,], Lat=tmp$Lat, Lon=tmp$Lon) %>% 
      rbind(., match_pre)
  } else { #  Fail exact match
    print(paste("Failed", tmp$Fail))
    unmatch_pre <- cbind(foo2[i,], tmp) %>% 
      rbind(., unmatch_pre)
  }
}

#     Combine all for final set

foo2 <- rbind(match_numb, match_pre, match_type) %>% 
  select(-starts_with("pm"), -Fail)

Old2 <- match %>% 
  select(-starts_with("pm")) %>% 
  rbind(., foo2)
  
Old_data <- sf::st_transform(
                sf::st_as_sf(Old2, coords = c("Lon", "Lat"), crs = google_crs),
                  crs=CoH_crs)

leaflet::leaflet() %>% 
  leaflet::addTiles() %>% # OpenStreetMap by default
  # leaflet::addPolygons(data=sf::st_transform(Old_data, crs=google_crs),
  #                  color="blue",
  #                  opacity=1,
  #                  weight=.5,
  #                  popup = ~osm_id,
  #                  fillOpacity = 0.5) %>% 
  leaflet::addCircleMarkers(data=sf::st_transform(Old_data,crs=google_crs), 
                   popup = ~as.character(yr_impr),
                   radius=2, 
                   color="black",
                   opacity=1,
                   fillOpacity = 1)
```















